---
title: "BOJfame"
output:
  github_document:
    fig_width: 8
    fig_height: 4
---

The `BOJfame` package provides an `R` interface to the Bank of Japan's [Time-Series Data Search](https://www.stat-search.boj.or.jp/index_en.html) portal. Specifically, it allows users to download individual series codes directly from within R using exact series codes.

The name derives from the "famecgi2" script underpinning the BOJ's database system; most likely this is a reference to the [FAME](https://en.wikipedia.org/wiki/FAME_(database)) database tool.

## Install package

The package can be installed from Github.

```{r install, eval=FALSE, message=FALSE, warning=FALSE}
library(devtools)
install_github("stefanangrick/BOJfame")  # GitHub
```

## Example usage

To import data, first load the package.

```{r loading, message=FALSE, warning=FALSE}
library("BOJfame")
```

Next, we run the `get_bojfame()` function to download two data series. Note that data series need to be of the same frequency, otherwise an error is returned. In the example below, we download two daily-frequency time series. We use `start_year` and `end_year` to specify the desired date range.

```{r datasets, message=FALSE, warning=FALSE}
bojdata <- get_bojfame(series_codes = c("FM01'STRDCLUCON", "IR01'MADR1Z@D"),
                       start_year = 1995, end_year = 2022)
```

The `get_bojfame()` function returns a list with a [tibble](https://tibble.tidyverse.org/) data frame holding the actual data. Access the data using `$data` variable.

```{r data, message=FALSE, warning=FALSE}
bojdata$data
```

Use `$meta` to access a [tibble](https://tibble.tidyverse.org/) data frame holding relevant meta data.

```{r meta, message=FALSE, warning=FALSE}
bojdata$meta
```

To plot the data using [ggplot2](https://ggplot2.tidyverse.org), run the below.

```{r plot, message=FALSE, warning=FALSE}
library("dplyr")
library("ggplot2")

bojdata$data <- mutate(bojdata$data,
                       indicator = recode(indicator,
                                          "FM01'STRDCLUCON" = "Call rate",
                                          "IR01'MADR1Z@D" = "Basic loan rate"))

ggplot(bojdata$data, aes(x = date, y = obs_value)) +
  geom_line(aes(colour = indicator)) +
  labs(title = "Interest rates", x = "Date", y = "%") +
  theme(legend.title = element_blank())
```

Note that BOJ data sets come with a number of different time formats. The [zoo](https://cran.r-project.org/package=zoo) package (e.g. `as.yearmon()`) should be able to parse most formats.

## Note

This package is in no way officially related to or endorsed by the [Bank of Japan](https://www.boj.or.jp/). Please don't abuse the BOJ's servers with unnecessary calls.
